Palmer amaranth (\emph{Amaranthus palmeri}) adaptation to agroecossystems

### 2021-07-30 Manuscript/Manuscript.Rmd
,M,

```{r fig2, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/Combined2.png")
```

@@

```{r fig3, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/figure 3.png")
```

@@

```{r, Figure-2, ref.label = "fig2", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second transplant timing (B)', out.width = "160mm", out.height = "130mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

>>>>

```{r fig2, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/Figure 2.png")
```

@@

```{r fig3, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/Figure 3.png")
```

@@

```{r, Figure-2, ref.label = "fig2", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second transplant timing (B)', out.width = "130mm", out.height = "130mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

### 2021-07-30 Manuscript/Manuscript.tex
,M,

Palmer amaranth (\emph{Amaranthus palmeri} S. Watson) is currently
considered one of the most economically damaged weed species to cropping
systems in the United States (Ward et al., 2013). The species has showed
a remarkable capacity to evolve resistance to herbicides. Palmer
amaranth has evolved resistance to eight herbicide sites of action
(Heap, 2021), increasing the weed management complexity (Lindsay et al.,
2017). Uncontrolled Palmer amaranth in competition for water, light and
nutrients can drastically reduce crop yields (Berger et al., 2015).
Palmer amaranth is documented with potential to reduce 91\%, 68\%, and
54\% of corn (Massinga et al., 2001), soybean (Klingaman and Oliver,
1994), and cotton (Morgan et al., 2001) yields, respectively.

@@

@@

Palmer amaranth cumulative flowering from first transplant timing ranged
from late June to early September. Palmer amaranth growing in corn
resulted in a longer flowering pattern compared to fallow and soybean.
Palmer amaranth reached 10\% flowering in soybean at doy 180, which was
slightly different from fallow (doy 180.9; \emph{P} = 0.01) and corn
(doy 181.7; \emph{P} = 0.00). Nonetheless, the 10\% cumulative Palmer
amaranth flowering in soybean, fallow and corn occurred at the end of
June. The 50\% Palmer amaranth cumulative flowering occurred in July.
For example, Palmer amaranth reached 50\% in fallow at doy 193.4,
followed by soybean (doy 194.8), corn (doy 206.6). Similar trend was
observed at 90\% Palmer amaranth cumulative flowering. Palmer amaranth
growing in corn reached 90\% flowering at doy 252.6 (early September),
which was 37.8 and 32.2 days after Palmer amaranth 90\% flowering in
fallow and soybean, respectively.

Palmer amaranth cumulative flowering from second transplanting timing
ranged from mid July to mid September. All cumulative flowering
comparisons among agroecossystems were significant (\emph{P} \textless{}
0.00) Palmer amaranth growing in fallow resulted in earlier flowering
time compared to soybean and corn. Palmer amaranth growing in fallow
reached 10\%, 50\%, and 90\% flowering time at day 203.8, 214.4, and
232.2, respectively. Palmer amaranth growing in soybean reached 10\%
flowering at doy 210.9, which was 6 days prior to corn (\emph{P}-value =
0.00). Similar trend was observed at 50\% flowering, whereas Palmer
amaranth reached 50\% flowering in corn (doy 233.0) 4 days after
soybeans (doy 228.9; \emph{P} = 0.00). The 90\% Palmer amaranth
cumulative flowering occurred at same day in corn (260.9) and soybean
(260.5; \emph{P} = 0.66).

@@

{\centering \includegraphics[width=160mm,height=130mm]{../data analysis/figures/Combined2}

@@

{\centering \includegraphics[width=130mm,height=70mm]{../data analysis/figures/figure 3}

>>>>

Palmer amaranth (\emph{Amaranthus palmeri} S. Watson) is currently
considered one of the most economically damaged weed species to cropping
systems in the United States (Ward et al., 2013). The species has showed
a remarkable capacity to evolve resistance to herbicides. Palmer
amaranth has evolved resistance to eight herbicide sites of action
(Heap, 2021), increasing the weed management complexity (Lindsay et al.,
2017). Uncontrolled Palmer amaranth in competition for water, light and
nutrients can drastically reduce crop yields (Berger et al., 2015).
Palmer amaranth is documented with potential to reduce 91\%, 68\%, and
54\% of corn (Massinga et al., 2001), soybean (Klingaman and Oliver,
1994), and cotton (Morgan et al., 2001) yields, respectively. Thus,
Palmer amaranth poses a risk to sustainable agriculture.

@@

Monthly mean air temperature and sum precipitation were obtained using
Daymet weather data from June through September across the five
locations in 2018 and 2019 (\textbf{correndo2021?}) (Figure 1)

@@

Palmer amaranth cumulative flowering from first transplant timing ranged
from late June to early September (Figure 2). Palmer amaranth growing in
corn resulted in a longer flowering pattern compared to fallow and
soybean. Palmer amaranth reached 10\% flowering in soybean at doy 180,
which was slightly different from fallow (doy 180.9; \emph{P} = 0.01)
and corn (doy 181.7; \emph{P} = 0.00). Nonetheless, the 10\% cumulative
Palmer amaranth flowering in soybean, fallow and corn occurred at the
end of June. The 50\% Palmer amaranth cumulative flowering occurred in
July. For example, Palmer amaranth reached 50\% in fallow at doy 193.4,
followed by soybean (doy 194.8), corn (doy 206.6). Similar trend was
observed at 90\% Palmer amaranth cumulative flowering. Palmer amaranth
growing in corn reached 90\% flowering at doy 252.6 (early September),
which was 37.8 and 32.2 days after Palmer amaranth 90\% flowering in
fallow and soybean, respectively.

Palmer amaranth cumulative flowering from second transplanting timing
ranged from mid July to mid September (Figure 2). All cumulative
flowering comparisons among agroecossystems were significant (\emph{P}
\textless{} 0.00) Palmer amaranth growing in fallow resulted in earlier
flowering time compared to soybean and corn. Palmer amaranth growing in
fallow reached 10\%, 50\%, and 90\% flowering time at day 203.8, 214.4,
and 232.2, respectively. Palmer amaranth growing in soybean reached 10\%
flowering at doy 210.9, which was 6 days prior to corn (\emph{P}-value =
0.00). Similar trend was observed at 50\% flowering, whereas Palmer
amaranth reached 50\% flowering in corn (doy 233.0) 4 days after
soybeans (doy 228.9; \emph{P} = 0.00). The 90\% Palmer amaranth
cumulative flowering occurred at same day in corn (260.9) and soybean
(260.5; \emph{P} = 0.66).

@@

{\centering \includegraphics[width=130mm,height=130mm]{../data analysis/figures/Figure 2}

@@

{\centering \includegraphics[width=130mm,height=70mm]{../data analysis/figures/Figure 3}
